\huge{Comment on `The Limits of Cosmic Shear'}

### 2016-11-25 Limber_Comment.tex
First draft at intro and cfhtlens section

\begin{abstract}
Kitching et al. (2016) examine the impact of four approximations that can be used when constraining cosmological parameters from the measurement of weak gravitational lensing by large-scale structures, also known as cosmic shear.  We support the core important message of this paper that such approximations should not be used for the future analysis of high precision surveys such as Euclid, LSST and WFIRST.  In this comment, we argue that these approximations are not able to explain away the tension between the constraints from some current weak lensing surveys and Planck.  Reducing uncertainty and characterising bias and in photometric redshift estimation is certainly a crucial task for the success of current and future surveys.  We highlight that sophisticated treatments of these uncertainties have already been explored in the literature and have been shown not to resolve the tension with Planck, in contrast to the message that Kitching et al. (2016) convey.

@@

In this comment paper we discuss four approximations that can be used when deriving theoretical predictions for the principally used cosmic shear statistic, $\xi_\pm$, the two-point shear correlation function.   These approximations have been explored in (ADD REF) and most recently highlighted by \citet{kitching/etal:2016} as a way to reduce tensions between weak lensing and CMB experiments, focusing on a re-analysis of the non-tomographic weak lensing data from the CFHTLenS survey \citet{kilbinger/etal:2013}.    In section~\ref{sec:cfhtlens} we compare the `one-parameter' cosmological re-analysis of \citet{kitching/etal:2016} with the full six-parameter analysis by \citet{kilbinger/etal:2013}, arguing that this particular non-tomographic data set is not in significant tension with Planck.  We also briefly review the literature that has advanced our understanding since the original CFHTLenS analyses were published.  In section~\ref{sec:theory} we clarify that only one/two? of the approximations highlighted by \citet{kitching/etal:2016} have actually been used in recent weak lensing analyses \citet{joudaki/etal:2016, hildebrandt/etal:2016, joudaki/etal:2017} and discuss why we do not expect these approximations to impact on the cosmological analysis of these surveys.    Finally in section~\ref{sec:photoz} we review our current knowledge of photometric redshift uncertainties and the sophisticated mitigation strategies that have already been applied to data from CFHTLenS, DES and KiDS.  We suggest that a possible misinterpretation in the direction of the redshift biases reported in \citet{choi/etal:2016} has lead to the incorrect conclusion of \citet{kitching/etal:2016} that these redshift biases can resolve the tension with Planck.

@@

\section{CFHTLenS:The Canada-France-Hawaii Telescope Lensing Survey}
\label{sec:cfhtlens}
\input{cfhtlens.tex}

>>>>

\begin{abstract}
Kitching et al. (2016) examine the impact of four approximations that can be used when constraining cosmological parameters from the measurement of weak gravitational lensing by large-scale structures, also known as cosmic shear.  We support the core important message of this paper that the use of such approximations should be carefully considered in the future analysis of high precision surveys such as Euclid, LSST and WFIRST.  In this comment, we argue that these approximations are not able to explain away the tension between the constraints from some current weak lensing surveys and Planck.  Reducing uncertainty and characterising bias in photometric redshift estimation is certainly a crucial task for the success of current and future surveys.  We highlight that sophisticated treatments of these uncertainties have already been explored in the literature and have been shown not to resolve the tension with Planck, in contrast to the message that Kitching et al. (2016) convey.

@@

In this comment paper we discuss four approximations that can be used when deriving theoretical predictions for the principally used cosmic shear statistic, $\xi_\pm$, the two-point shear correlation function.   These approximations have been explored in (ADD REF) and most recently highlighted by \citet{kitching/etal:2016} as a way to reduce tensions between weak lensing and CMB experiments, focusing on a re-analysis of the non-tomographic weak lensing data from the CFHTLenS survey \citep{kilbinger/etal:2013}.    In section~\ref{sec:cfhtlens} we compare the `one-parameter' cosmological re-analysis of \citet{kitching/etal:2016} with the full six-parameter analysis by \citet{kilbinger/etal:2013}, arguing that this particular non-tomographic data set is not in significant tension with Planck.  We also briefly review the literature that has advanced our understanding since the original CFHTLenS analyses were published.  In section~\ref{sec:theory} we clarify that only one/two? of the approximations highlighted by \citet{kitching/etal:2016} have actually been used in recent weak lensing analyses \citep{joudaki/etal:2016, hildebrandt/etal:2016, joudaki/etal:2017} and discuss why we do not expect these approximations to impact on the cosmological analysis of these surveys.    Finally in section~\ref{sec:photoz} we review our current knowledge of photometric redshift uncertainties and the sophisticated mitigation strategies that have already been applied to data from CFHTLenS, DES and KiDS.  We suggest that a possible misinterpretation in the direction of the redshift biases reported in \citet{choi/etal:2016} has lead to the incorrect conclusion of \citet{kitching/etal:2016} that these redshift biases can resolve the tension with Planck.

@@

\section{Advances in understanding since CFHTLenS}
\label{sec:cfhtlens}
\input{cfhtlens.tex}
